An exact Riemann solver for one-dimensional multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-06-04 Manuscript_revise.tex
eee

\begin{abstract} 
  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model \cite{wilkins1963calculation} and  the von Mises' yielding condition is studied in this paper. Through a detailed analysis of the Jacobian and eigenvectors, and the exact relations across different waves, an exact solution is constructed with three-to-five waves and thirty-six possible structure cases. More over, some useful results are also obtained in the analysis, for example, the significant jump of the sonic speed

  A multi-material HLLC-type  approximate Riemann solver with both elastic and plastic waves (MHLLCEP) is constructed for 1D elastic-plastic flows with the  hypo-elastic model and the von Mises yielding condition. Although Cheng in 2016 introduced a HLLC Riemann solver with elastic waves(HLLCE) for 1D elastic-plastic flows, Cheng assumed that pressure is continuous across the contact wave. This assumption maybe lead to big errors, especially for multi-material elastic-plastic flows. In our MHLLCEP, this assumption is not used again, and correspondingly the errors introduced by the assumption are deleted, describing and evaluating the plastic waves are more accurate than that in the HLLCE. Moreover, if the non-linear waves in the Riemann problem are only shock waves, even with the plastic waves, our MHLLCEP is theoretically accurate. For  the multi-material system, in this paper, a ghost cell method is used to achieve a high-order spatial reconstruction across the interface without numerical oscillations. Based on the MHLLCEP, combining with the third-order WENO reconstruction method and the third-order Runge-Kutta method in time, a high-order cell-centered Lagrangian scheme for 1D multi-material elastic-plastic flows is built in this paper. A number of numerical experiments are carried out. Numerical results show  that the presented third-order scheme is convergent, robust, and essentially non-oscillatory. Moreover, for multi-material elastic-plastic flows, the scheme with  the MHLLCEP is more accurate and reasonable in resolving the multi-material interface than the scheme with the  HLLCE.
\end{abstract}

>>>>

\begin{abstract} 
  The Riemann problem for one-dimensional  multi-material elastic-plastic flows with the Mie-Gr\"uneisen EOS, hypo-elastic constitutive model and  the von Mises' yielding condition is studied in this paper.  Through a detailed analysis of the Jacobian matrix and relations across different type of waves,  an exact Riemann solver is constructed with totally thirty-six possible cases of structure.  Some useful results are also obtained in the analysing, for example, the sonic speed experiences a significant jump when the material is yielding and the plastic wave is always faster than the elastic wave.  More over, an exact Riemann solver is also deduced for the half Riemann problem. A lot of examples show that, the results taken by the exact Riemann solver are in good agreement with those computed by the mumerical method.

\end{abstract}
